---
title: "Conjoint_presentation_design"
author: "Peder M Isager"
date: "August 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Conjoint presented as table

```{r, echo=FALSE}
options(scipen=999) # Prevent scientific notation

# Number of subjects

nsubs <- c(10, 100, 1000, 10000)

# Citation count

citcount <- c(0, 1, 10, 100, 1000)

# Altmetrix score

altmetric <- c(0, 1, 10, 100, 1000)

# The Journal the study is published in (ranked by impact factor)

journal <- c("Science (34.7)", "Psychological Science (7.4)", "British Journal of Psychology (1.6)", "Current Psychology (0.4)")

# Reported on in major news outlet

newsrep <- c("yes", "no")

# Foundation for practical innovation (e.g. education tool, therapy, public policy)

practical <- c("yes", "no")

# Is included in psych textbooks

inbooks <- c("yes", "no")

# Estimate precision

precision <- c() # Use confidence interval plots as stimuli? 

# Number of replications 

nreps <- c(0, 1, 10)

# Conflicting evidence 

conflict <- c("yes", "no")

# Cost of conducting replication

costUSD <- c(1000, 10000, 100000)

# Contains reporting error

reperror <- c("none", "minor", "major")

# Literature the study is from displays high rates of QRPs

qrpinlit <- c("rare", "somewhat common", "very common")

```


### All in one table 

| Attribute | Level | Attribute | Level |
| :--- | :--- | :--- | :--- |
| **Citation count** | `r sample(citcount, 1)` | **Citation count** | `r sample(citcount, 1)` |
| **Altmetric score** | `r sample(altmetric, 1)` | **Altmetric score** | `r sample(altmetric, 1)` |
| **Subjects tested** | `r sample(nsubs, 1)` | **Subjects tested** | `r sample(nsubs, 1)` |
| **Reported on in the news** | `r sample(newsrep, 1)` | **Reported on in the news** | `r sample(newsrep, 1)` |


## Two tables separated by css code

<table>
<tr><th>Option 1 </th><th>Option 2</th></tr>
<tr><td>

| Attribute | Level |
| :--- | :--- |
| **Citation count** | `r sample(citcount, 1)` |
| **Altmetric score** | `r sample(altmetric, 1)` |
| **Subjects tested** | `r sample(nsubs, 1)` |
| **Reported on in the news** | `r sample(newsrep, 1)` |

</td><td>

| Attribute | Level |
| :--- | :--- |
| **Citation count** | `r sample(citcount, 1)` |
| **Altmetric score** | `r sample(altmetric, 1)` |
| **Subjects tested** | `r sample(nsubs, 1)` |
| **Reported on in the news** | `r sample(newsrep, 1)` |

</td></tr> </table>

## Merged data.frames using knitr::kable()

```{r, echo=FALSE}
Attributes <- c("Citation count", "Altmetric", "Subjects", "In news")
Values <- c(sample(citcount, 1), sample(altmetric, 1), sample(nsubs, 1), sample(newsrep, 1))
option1 <- data.frame(Attributes, Values)

Attributes <- c("Citation count", "Altmetric", "Subjects", "In news")
Values <- c(sample(citcount, 1), sample(altmetric, 1), sample(nsubs, 1), sample(newsrep, 1))
option2 <- data.frame(Attributes, Values)

knitr::kable(list(option1, option2))
```
